Renewal and stability in populations structured by remaining years of life

### 2016-02-01 ThanoRepro/ThanoRepro.tex
.

In this paper, I explore some formal demographic consequences of a particular
redefinition of age. Instead of counting age as the time passed since birth,
consider the amount of time left until death.\footnote{Elsewhere this quantity
is referred to as \textit{residual} lifetime, time-to-death (TTD), prospective
age \citep{sanderson2007new}, or thanatological age \citep{riffe2015force}.}
Individuals in this case move in the same direction along imaginary life lines,
but the reference point for measurement is switched from birth to death. For
individuals, the timing of events in life is exactly identified using either of
years lived or left, but aggregate patterns differ.
%Temporal perspectives and rescalings of the lifecourse are abundant in
% demography already. Such work has enriched the discipline by producing new
% insights, questions, and conundrums.
% Fertility and reproduction are plausibly a function of both age perspectives,
 % and the question of how to best partition them over time is not investigated here.

>>>>

In this paper, I explore some formal demographic consequences of a particular
redefinition of age. Instead of counting age as the time passed since birth,
consider the amount of time left until death.\footnote{Elsewhere this quantity
is referred to as \textit{residual} life, time-to-death (TTD), prospective
age \citep{sanderson2007new}, or thanatological age \citep{riffe2015force}.}
Individuals in this case move in the same direction along imaginary life lines,
but the reference point for measurement is switched from birth to death. For
individuals, the timing of events in life is exactly identified using either of
years lived or left, but aggregate patterns differ.
%Temporal perspectives and rescalings of the lifecourse are abundant in
% demography already. Such work has enriched the discipline by producing new
% insights, questions, and conundrums.
% Fertility and reproduction are plausibly a function of both age perspectives,
 % and the question of how to best partition them over time is not investigated here.
